---
title: "TITLE TBD"
bibliography: refs.bib
csl: jama.csl
always_allow_html: true
output: 
  officedown::rdocx_document:
    reference_docx: style_manuscript_times_new_roman.docx
    keep_md: false
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      dpi = 600, 
                      fig.width = 11, 
                      fig.height = 6)

margins_normal <- page_mar(bottom = 1,  #0.3937, 
                           top    = 1,  #0.3937, 
                           right  = 1,  #0.3937, 
                           left   = 1, #0.3937,
                           gutter = 0)

portrait_above <- function(){
  
  block_section(
    prop_section(
      page_size = page_size(orient = "portrait"),
      type = "continuous",
      page_margins = margins_normal
    )
  )
  
}

landscape_above <- function(){
  block_section(
    prop_section(
      page_size = page_size(orient = "landscape"),
      page_margins = margins_normal,
      type = "continuous"
    )
  )
}


withr::with_dir(
 new = here::here(),
 code = {
  targets::tar_load(
   c(
    nhanes_design,
    tbl_characteristics,
    tbl_bp_means,
    tbl_htn_prev,
    tbl_htn_aware_prev,
    tbl_htn_aware_meds_prev,
    tbl_bp_control_prev,
    tbl_bp_control_meds_prev,
    tbl_prevalence_ratios,
    tbl_prevalence_ratios_by_cycle,
    tbl_prevalance_ratio_diffs
   )
  )
 }
)

width_max_landscape <- 10.5
width_max_portrait <- 7.5
 

```


```{r manuscript-globals}

htn_jnc7_defn <- "Hypertension was defined according to the Seventh Report of the Joint National Committee on Prevention, Detection, Evaluation, and Treatment of High Blood Pressure as a systolic blood pressure ≥ 140 mm Hg, and/or diastolic blood pressure ≥ 90 mm Hg and/or self-reported antihypertensive medication use."

htn_accaha_defn <- "Hypertension was defined according to the 2017 American College of Cardiology / American Heart Association Blood Pressure Guideline as a systolic blood pressure ≥ 130 mm Hg, and/or diastolic blood pressure ≥ 80 mm Hg and/or self-reported antihypertensive medication use."

bpc_jnc7_defn <- "Controlled blood pressure was defined as systolic blood pressure < 140 mm Hg and diastolic blood pressure < 90 mm Hg."

bpc_accaha_defn <- "Controlled blood pressure was defined as systolic blood pressure < 130 mm Hg and diastolic blood pressure < 80 mm Hg."


age_wts_rounded <- round(100*nhanes_design$wts_overall, 2)

age_wts_defn_overall <- glue(
 "Age adjustment was performed using direct standardization with the standard \\
 being all adults across the entire period (2013-2023); the age categories \\
 used for standardization were \\
 18 to 44 years ({age_wts_rounded[1]}%), \\
 45 to 64 years ({age_wts_rounded[2]}%), \\
 65 to 74 years ({age_wts_rounded[3]}%), \\
 and 75 years or older ({age_wts_rounded[4]}%)."
)

age_wts_rounded <- round(100*nhanes_design$wts_htn, 2)

age_wts_defn_htn <- glue(
 "Age adjustment was performed using direct standardization with the standard \\
 being all adults with hypertension across the entire period (2013-2023); \\
 the age categories used for standardization were \\
 18 to 44 years ({age_wts_rounded[1]}%), \\
 45 to 64 years ({age_wts_rounded[2]}%), \\
 65 to 74 years ({age_wts_rounded[3]}%), \\
 and 75 years or older ({age_wts_rounded[4]}%)."
) 
```


Table 1. Demographic characteristics of US adults in 2013-2014, 2015-2016, 2017-2020, and 2021-2023.

```{r}
flextable_autofit(tbl_characteristics, 
                  prop_used_col_1 = .3,
                  width_max = width_max_portrait) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population."
 ))
```

`r portrait_above()`

Table 2. Age-specific and age-adjusted prevalence of hypertension among US adults in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in age, sex, and race-ethnicity subgroups.

```{r}
flextable_autofit(tbl_htn_prev$jnc7,
                  prop_used_col_1 = .3,
                  width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population or subgroup with hypertension."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_jnc7_defn)) %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_overall))

```

\newpage

Table 3. Age-specific and age-adjusted proportion of US adults with hypertension who had controlled blood pressure in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in subgroups.

```{r}
flextable_autofit(tbl_bp_control_prev$jnc7,
                  prop_used_col_1 = .3,
                  width_max = width_max_landscape)  %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population with hypertension who had controlled blood pressure."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_jnc7_defn)) %>%
 add_footer_lines(values = as_paragraph(bpc_jnc7_defn)) %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_htn))
```

\newpage

Table 4. Age-specific and age-adjusted proportion of US adults with hypertension and taking antihypertensive medication who had controlled blood pressure in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in subgroups.

```{r}
flextable_autofit(tbl_bp_control_meds_prev$jnc7,
                  prop_used_col_1 = .3,
                  width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population with hypertension and taking antihypertensive medication who had controlled blood pressure."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_jnc7_defn)) %>%
 add_footer_lines(values = as_paragraph(bpc_jnc7_defn)) %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_overall))
```


`r landscape_above()`

Table 5: Prevalence ratios for blood pressure control by calendar period among adults with hypertension.

```{r}
tbl_prevalence_ratios_by_cycle$htn %>% 
 flextable_autofit(prop_used_col_1 = .3, 
                   width_max = width_max_portrait) %>%
 add_footer_lines(values = as_paragraph("Multivariable adjustment was applied using all variables listed in the table")) %>% 
 add_footer_lines(values = as_paragraph(bpc_jnc7_defn))
 
```

\newpage

Table 6: Prevalence ratios for blood pressure control by calendar period among adults with hypertension taking antihypertensive medication.

```{r}
tbl_prevalence_ratios_by_cycle$htn_med_use %>% 
 flextable_autofit(prop_used_col_1 = .3, 
                   width_max = width_max_portrait) %>%
  add_footer_lines(values = as_paragraph("Multivariable adjustment was applied using all variables listed in the table")) %>% 
 add_footer_lines(values = as_paragraph(bpc_jnc7_defn))
 
```

`r portrait_above()`

**SUPPLEMENT**

\newpage

Table S1. Mean systolic and diastolic blood pressure and distribution of blood pressure categories among US adults in 2013-2014, 2015-2016, 2017-2020, and 2021-2023.

```{r}
flextable_autofit(tbl_bp_means,
                  prop_used_col_1 = .3, 
                  width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph("Numbers in the table are estimated mean or percentage (95% confidence interval) of the US adult population.")) %>% 
 add_footer_lines(values = as_paragraph("US adults with systolic and diastolic blood pressure in two categories were categorized according to the higher grouping (e.g., a participant with systolic blood pressure of 124 mm Hg and diastolic blood pressure of 84 mm Hg were placed in the 130-139/80-89 mm Hg category)."))
```


\newpage

Table S2: Age-specific and age-adjusted proportion of US adults with hypertension who reported being aware they had hypertension in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in subgroups.
```{r}
flextable_autofit(tbl_htn_aware_prev$jnc7,
                  prop_used_col_1 = .3,
                  width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population with hypertension who reported being aware they had hypertension."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_jnc7_defn)) %>%
 add_footer_lines(values = as_paragraph(age_wts_defn_htn))

```

\newpage

Table S3: Age-specific and age-adjusted proportion of US adults with and aware of having hypertension who were taking antihypertensive medication in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in subgroups.
```{r}
flextable_autofit(tbl_htn_aware_meds_prev$jnc7,
                  prop_used_col_1 = .3,
                  width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are proportion (95% confidence interval) of the population with and aware of having hypertension that reported taking antihypertensive medication"
 )) %>%
 add_footer_lines(values = as_paragraph(htn_jnc7_defn)) %>%
 add_footer_lines(values = as_paragraph(age_wts_defn_htn))

```


`r landscape_above()`

Table S4: Prevalence ratios for hypertension awareness and antihypertensive medication use

```{r}

tbl_prevalence_ratios$awareness_meds %>% 
 flextable_autofit(prop_used_col_1 = .3, 
                   width_max = width_max_portrait)

```

`r portrait_above()`

Table S5. Age-adjusted prevalence of hypertension among US adults in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in age, sex, and race-ethnicity subgroups without calibrating the oscillometric blood pressure measurements.

```{r}

flextable_autofit(tbl_htn_prev$jnc7_uncalib,
                  prop_used_col_1 = .3,
                  width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population or subgroup with hypertension."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_jnc7_defn)) %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_overall))

```

\newpage

Table S6. Age-specific and age-adjusted proportion of US adults with hypertension who had controlled blood pressure according to the JNC7 guideline in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in subgroups, without calibrating the oscillometric blood pressure measurements.

```{r}
flextable_autofit(tbl_bp_control_prev$jnc7_uncalib,
                  prop_used_col_1 = .3,
                  width_max = width_max_landscape)  %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population with hypertension who had controlled blood pressure."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_jnc7_defn)) %>%
 add_footer_lines(values = as_paragraph(bpc_jnc7_defn))  %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_htn))
```


\newpage

Table S7. Age-specific and age-adjusted proportion of US adults with hypertension and taking antihypertensive medication who had controlled blood pressure according to the JNC7 guideline in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in subgroups, without calibrating the oscillometric blood pressure measurements.
```{r}
flextable_autofit(tbl_bp_control_meds_prev$jnc7_uncalib,
                  prop_used_col_1 = .3,
                  width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population with hypertension and taking antihypertensive medication who had controlled blood pressure."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_jnc7_defn)) %>%
 add_footer_lines(values = as_paragraph(bpc_jnc7_defn))  %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_htn))
```

\newpage

Table S8: Age-specific and age-adjusted prevalence of hypertension defined by the 2017 ACC/AHA Blood Pressure Guideline among US adults in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in subgroups.

```{r}
tbl_htn_prev$accaha %>% 
 flextable_autofit(prop_used_col_1 = .3,
                   width_max = width_max_landscape)  %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population or subgroup with hypertension."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_accaha_defn)) %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_overall))
```

\newpage

Table S9: Age-specific and age-adjusted proportion of US adults with hypertension according to the 2017 ACC/AHA BP guideline who were aware they had hypertension in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in subgroups.

```{r}
tbl_htn_aware_prev$accaha %>% 
 flextable_autofit(prop_used_col_1 = .3,
                   width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population with hypertension who were aware they had hypertension."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_accaha_defn)) %>%
 add_footer_lines(values = as_paragraph(bpc_accaha_defn))  %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_htn))
```

\newpage

Table S10: Age-specific and age-adjusted proportion of US adults aware they had hypertension according to the 2017 ACC/AHA BP guideline who were taking antihypertensive medication in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in subgroups.

```{r}
tbl_htn_aware_meds_prev$accaha %>% 
 flextable_autofit(prop_used_col_1 = .3,
                   width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population with hypertension and aware of having hypertension who reported using antihypertensive medication."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_accaha_defn)) %>%
 add_footer_lines(values = as_paragraph(bpc_accaha_defn)) %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_htn))
```

\newpage

Table S11. Age-specific and age-adjusted proportion of US adults with hypertension who had controlled blood pressure according to the 2017 ACC/AHA Blood Pressure Guideline in 2009-2012, 2013-2016 and 2017-2020, overall and in subgroups.

```{r}
flextable_autofit(tbl_bp_control_prev$accaha,
                  prop_used_col_1 = .3,
                  width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population with hypertension who had controlled blood pressure."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_accaha_defn)) %>%
 add_footer_lines(values = as_paragraph(bpc_accaha_defn)) %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_htn))
```

\newpage

Table S12. Age-specific and age-adjusted proportion of US adults with hypertension  and taking antihypertensive medication who had controlled blood pressure according to the 2017 ACC/AHA BP guideline in 2013-2014, 2015-2016, 2017-2020, and 2021-2023, overall and in subgroups.

```{r}

tbl_bp_control_meds_prev$accaha %>% 
 flextable_autofit(prop_used_col_1 = .3,
                   width_max = width_max_landscape) %>% 
 add_footer_lines(values = as_paragraph(
  "Numbers in the table are estimated percentage (95% confidence interval) of the US adult population with hypertension and taking antihypertensive medication who had controlled blood pressure."
 )) %>% 
 add_footer_lines(values = as_paragraph(htn_accaha_defn)) %>%
 add_footer_lines(values = as_paragraph(bpc_accaha_defn)) %>% 
 add_footer_lines(values = as_paragraph(age_wts_defn_htn))

```

`r landscape_above()`

Table S13. Percent of increase in blood pressure control from 2017-2020 to 2021-2023 among non-Hispanic Black adults that can be attributed to education, income-to-poverty ratio, routine place for health care and type of health insurance.

```{r}
tbl_prevalance_ratio_diffs %>% 
 flextable_autofit(prop_used_col_1 = .3)
```


\newpage

Exclusion Table: Participants included in the current analysis. (Left this un-numbered to keep the same supplemental table numbers as the analysis plan)

```{r}

read_csv(here::here('doc/exclusions.csv')) %>% 
 rename(Overall = overall) %>% 
 rename_with(.fn = ~str_replace(.x, "_", "-")) %>% 
 flextable() %>% 
 flextable_polish() %>% 
 set_header_labels(label = "Exclusion") %>% 
 add_header_row(values = c("Exclusion",
                           "Overall",
                           "Calendar period"),
                colwidths = c(1, 1, 4)) %>% 
 merge_v(part = 'header') %>% 
 flextable_autofit(prop_used_col_1 = .3)

```


`r portrait_above()`



